\documentclass{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{blindtext}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}

\lstset{
    frame=single,
}

\title{Crypto - HW 4}
\author{Hagai Ben Yehuda, ID num: 305237000\\ Jonathan Bauch, ID num: 204761233}
\date{}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\interlinepenalty 10000
\begin{document}
  \maketitle

\section{} % 1
\lstinputlisting[language=Python, caption=Q1 Code]{Q1.sage}
\lstinputlisting[caption=Q1 Output]{Q1_output.txt}
\textbf{Explanation}: Any $a$ with an $i$ as defined in the question is a witness that $m$ is not prime. Define $b := a^{(m-1)/2^i}$.
b is square  root of $1$ $\pmod{m}$ because:
\[ b^2 = (a^{(m-1)/2^i})^2 = a^{(m-1)/2^{i-1}} \equiv 1 \pmod{m} \]
But $b \not \equiv \pm 1 \pmod{m}$, therefore the polynomial $(x-1)^2$ has more than $2$ roots in $\mathbb{Z}_m$, which implies that $\mathbb{Z}_m$ is not a field (otherwise it would be a contradiction to the fundamental theorem of algebra). Therefore $m$ is not a power of a prime number, and specifically, it's not a prime number. 

\section{} % 2
We construct a randomized algorithm $A'$ that operates on input $m = pq$ as follows:
\begin{enumerate}
\item Draw $y\in Z_{m}^{*}$ uniformly (we do that by drawing from $\{1,...,m-1\}$ and making sure $\gcd(y,m)$ is $1$, if it isn't we can factor m using $y$). .
\item Execute $A$ on input $y^2 \pmod m $ and set $x$ to be its result (note that since $y^2 \pmod m $ is a quadratic residue we will get a number and not  "go catch a Stellagama stellio"). 
\item If $x = \pm y \pmod m$ and this step was executed less then $c$ times ($c$ being a constant positive integer that will affect the probability of success) go to step one. If this step was executed $c$ times, return $0$.
\item Calculate $w = x  y^{-1} \pmod m$.
\item Set $k = w+1 \pmod m$ 
\item Set $z = \frac{k}{2}$.
\item set $q = gcd(z, m)$ and return $(q, \frac{m}{q})$
\end{enumerate} 
We shall now prove that $A'$ runs in $O(t(n))$ and finds a factorization for $m$ with probability $ 1- \frac{1}{2^c}$.
First note that m executes steps 1 through 3 at most $c$ time (from the restriction in step 3) and each steps takes $O(t(n))$ steps.
In addition for each execution $A'$ passes step $3$ with probability $\frac{1}{2}$, that is because $y^2$ has four roots in $Z_{m}^{*}$, and only two of them are $\pm y$, since $y$ was chosen uniformly, the probability that the root that $A$ returns for $y^2$ is $ \pm y$  is  $\frac{2}{4} = \frac{1}{2}$.
Now we prove that if $A'$ passes step 3 it returns a correct factorization.

From the CRT we can write $x = wy$ with 
\[w = a_1(q^{-1} \pmod p)q + a_2(p^{-1} \pmod q)p\]
and $a_i \in \{\pm 1\}$ (this is because as stated in the lecture, if $x$ is a root of $y$ then it can be written as $ly$ with $l$ being a root of $1$ in $m$), since we chose x such that $x \neq \pm y$, we know that $a_1 \neq a_2$.\\
Assume without loss of generality that $a_1 = 1$ and  $a_2 = -1$, thus we have ( $w$ is from step 4)
\[w = (q^{-1} \pmod p)q - (p^{-1} \pmod q)p \]
Note that from fermat's little theorem we have 
\[(q^{-1} \pmod p)= q^{p-2} + cp\]
\[(p^{-1} \pmod q)= p^{q-2} + rq\]
Thus 
\[w = q^{p-1} - p^{q-1} \pmod {pq}\]
Note that 
\[q^{p-1} + p^{q-1} = 1 \pmod p\]
and
\[q^{p-1} + p^{q-1}  = 1 \pmod q\]
Hence
\[q^{p-1} + p^{q-1} \pmod {pq} = 1\]
Thus
\[w + 1 = q^{p-1} - p^{q-1} + 1  = q^{p-1} - p^{q-1} + q^{p-1} + p^{q-1} = 2q^{p-1} \pmod {pq}\]
Therefore when we calculate $z$ in step 6 we obtain $q^{p-1}$ and obviously $\gcd(q^{p-1}, pq) = q$, and thus we indeed recover q and p in step 7 as required, since we got to step 4 in $O(t(n))$ steps and 4 through 7 also take $O(t(n))$ steps, $A'$ is an algorithm as request.
Randomization is required in our algorithm as we must get a root that is differs from the root we know not only by sign. Since we have no knowledge of what root $A$ will return, and since we cant find another root by ourselves, we must hope $A$ returns a different root, by choosing $y$ randomly many times, the probability we will indeed find a root that is different not only by sign approaches $1$.
 

\section{} % 3
\lstinputlisting[language=Python, caption=Q3 Code]{Q3.sage}
\lstinputlisting[caption=Q3 Output, breaklines=true]{Q3_output.txt}

\subsection{} % 3.a
Based on the results of this small scale experiment we can recommend not to choose $c=0$ or $x_0=1,c=-1$ as the algorithm would fail to factor a big number as in our case (in reasonable time).
Other than that, for all the other values we tried, the time it took to factor $m$ was about $[0.3, 3] \cdot \sqrt{p}$ iterations, which is the expected average case for this algorithm. Without further investigation we cannot recommend particular values which would give good results for any values of $m$.

\subsection{} % 3.b
With the linear function $f(x)=x+c$ non of the program executions terminated (in the time frame of $5 m^{\frac{1}{4}}$ iterations). This is because the function $f$ is indeed not random at all. Observe that
$f^k(x) = x + k \cdot c$. The algorithm ends when:
\begin{align*}
     & gcd(m, y - x) \neq 1 \\
\iff & gcd(m, f^{2k}(x_0) - f^{k}(x_0)) \neq 1 \\
\iff & gcd(m, x_0 + 2kc - x_0 - kc) \neq 1 \\
\iff & gcd(m, kc) \neq 1
\end{align*}
Therefore it will halt only after $min\{p,q\}$ steps (unless $c \mid m$, which is unlikely).

\section{} % 4
\lstinputlisting[language=Python, caption=Q4 Code]{Q4.sage}
\pagebreak
\lstinputlisting[caption=Q4 Output]{Q4_output.txt}
\textbf{Explanation}: TODO
\subsection{} % 4.a
As hinted at the course forum (http://tau-crypto-f16.wikidot.com/forum/t-2034665/some-ex04-questions-for-q2-q4-and-q5) the way we chose the primes is as follows:
\begin{enumerate}
\item Get a random prime number $r$ of the requested size,
\item Calculate $s = 2r + 1$ 
\item Check if $s$ is also a prime:\\
 If it is - return it. \\
 Otherwise go the step $1$.
\end{enumerate}
In other words: $p, q$ were drawn randomly from the set $\left\{ x \in \mbox{Primes} \mid \frac{x-1}{2} \in \mbox{Primes} \right\}$, with the restriction on minimum size of the primes.

\subsection{} % 4.b
Required results are in Listing 6: Q4 Output.

\section{} % 5

We construct a polytime algorithm $A'$ that on input $p, g,g^x$ does the following:
\begin{itemize}
\item Draw $x\in \mathbb{Z^*}_{p}$ uniformly.
\item Execute $A$ on $p, g, g^{x+y}$ (note that $g^{x+y} = g^x g^y$), set $z$ to be the result.
\item  If $g^z = g^{x+y}$ return $z - y$, else if this is the 700'th time return 0, else go to the first step.
\end{itemize}
First note that this algorithm is polynomial as it executes $A$ at most 700 times, and $A$ is polynomial.
For each iteration the probability of landing within the subset of $x's$ for which $A$ finds and inverse is $\frac{1}{1000}$ as the sum of a uniform random variable and a constant is uniform. Hence with probability $\frac{1}{1000}$ we obtain the correct z in the last step, note that
\[g^{z-y} = g^z g^{-y} = g^{x+y}  g^{-y} = g^x\]
Thus $z-y$ is a solution to the DL problem.
The last step in $A$ fails only if $x+y$  is not inside the set for which $A$ solves the DL problem, this probability is $\frac{1}{1000}$ because $x+y$ distributes uniformly over $\mathbb{Z^*}_{p}$.

Because $A'$ makes 700 tries before returning with a false result, the probability that $A'$ fails is the probability that $A$ fails at each attempt which is $ (1-\frac{1}{1000})^{700} < \frac{1}{2}$.
Thus $A'$ is an algorithm as requested.

\section{} % 6

\subsection{} % 6.a
We construct a the decryption function:
\[
Dec(c_1, c_2) = 
\begin{cases}
	 1 &\mbox{if }  c_1^x = c_2 \\ 
	 0 &\mbox{else}
\end{cases} 
\]
If $b=0$, then $c_2 = h^y = g^{xy} = c_1^x $, thus if $b=0$ $Dec$ returns the correct result.\\
If $b=1$ then given $z$ there is exactly one value of $y$ for which $g^y = g^{zx}$ since $g$ is a multiplicative generator, if  $g^y = g^{zx}$ then $y = zx \pmod {p-1}$, the only case in which we decrypt a $1$ to $0$ is if $y = xz$ which happens with probability at most $\frac{1}{p - 1}$.
Thus correct and efficient decryption is possible except for a negligible probability.

\subsection{} % 6.b
Assume that this encryption scheme is not $\epsilon CPA$ secure, then there is a polynomial adversary $A$ that wins the adversarial indistinguishability test with probability $ > \frac{1}{2} + \epsilon$.
We construct a polynomial time adversary $A'$ that shows DDH is not hard:
Given input $(g^x,g^y,g^z)$ our algorithm does the following:
\begin{itemize}
\item Supply $A$ with $(p, g, g^x)$.
\item Get the two messages from $A$ assume WLOG $A$ replays with $m_0 = 0$, $m_1 = 1$ (if this is not the case we can construct an algorithm $B$ that is based on $A$ and wins with the same probability, since if the messages are in a different order $B$ can change the order and if both messages have the same value $A$ can only guess which bit was chosen as both will be encrypted to the same value and $B$ can supply us with two messages and also guess and win with the same probability).
\item Supply $A$ with $(g^y, g^z)$, if $A$ returns 1 return 0, else return 1.  
\end{itemize}
We shall now show that $A'$ distinguishes $(g^x,g^y,g^z)$ from $(g^x,g^y,g^{xy})$:
\begin{align*}
&\Pr_{x,y \leftarrow U_{\mathbb{Z^*}_{p}}, z= xy}(A'(g^x, g^y, g^{z}) = 1) - \Pr_{x,y,z \leftarrow U_{\mathbb{Z^*}_{p}}}(A'(g^x, g^y, g^z) = 1)\\
& = \Pr(A'(g^x, g^y, g^{z}) = 1| x,y \leftarrow U_{\mathbb{Z^*}_{p}}, z= xy) - \Pr(A'(g^x, g^y, g^z) = 1| x,y,z \leftarrow U_{\mathbb{Z^*}_{p}})\\
&= \Pr(A \mbox{  wins } | b = 1) - \Pr(A \mbox{  loses }| b = 0)\\
&= 2[\Pr(A \mbox{  wins } \cap b = 1) - \Pr(A \mbox{  loses }\cap b = 0)]\\
&= 2[\Pr(A \mbox{  wins } \cap b = 1) - \Pr(b = 0) + \Pr(A \mbox{  wins }\cap b = 0)]\\
&= 2[\Pr(A \mbox{  wins }) - \Pr(b = 0) ]\\
&\geq 2[\frac{1}{2} + \epsilon - \frac{1}{2}] = 2\epsilon
\end{align*}

Note that in our calculation we refer to the probability that $x,y,z$ are drawn uniformly or $z=xy$ (this is $b$ as defined in the adversarial indistinguishability test) , each case has probability $\frac{1}{2}$ as we are in a distinguisher setup and thus are supplied with a sample from each distribution with equal probability (otherwise the streams are distinguishable by always saying that the current input originated from the stream with higher probability to be sampled).
Thus $A'$ is a distinguisher as required.

\section{} % 7
Let $i \leftarrow U_t$ be the random index $A_1$ chooses. $b \leftarrow U_{0,1}$. $c^i = E_{pk}(m_b^i)$. Denote $A(x)$ the answer of an adversary $A$, given a cipher $x$. We have:
\begin{align*}
&\frac{1}{2} + \varepsilon \\
\mbox{(\ensuremath{\varepsilon}-CPA secure)} \ge &\Pr\left[\mbox{\ensuremath{A_1} wins}\right] \\
\mbox{(by definition)} = &\Pr\left[A_1(c^i)=b\right] \\
\mbox{(total probability)} = &\frac{1}{2} \sum_{d \in \{0,1\}} \Pr\left[A_1(c^i)=d \mid b=d\right] \\
\mbox{(total probability)} = &\frac{1}{2t} \sum_{d \in \{0,1\}} \sum_{k=1}^t \Pr\left[A_1(c^i)=d \mid b=d \wedge i=k\right] \\
\mbox{(by definition)} =  &\frac{1}{2t} \sum_{d \in \{0,1\}} \sum_{k=1}^t \Pr\left[A_1(E_{pk}(m_d^k))=d \mid b=d \wedge i=k\right] \\
\mbox{(by definition)} =  &\frac{1}{2t} \sum_{d \in \{0,1\}} \sum_{k=1}^t \Pr\left[A_{mult}\left(E_{pk}(m_0^1, \ldots, m_0^{k-1}, m_d^k, m_1^{k+1}, \ldots, m_1^t)\right)=d\right] \\
\mbox{(sum reorder)} = &\frac{1}{2t} \Bigg{(}
	\overbrace{\sum_{d \in \{0,1\}} \Pr\left[A_{mult}\left(E_{pk}(m_d^1, \ldots, m_d^t)\right)=d\right]}^{=2 \cdot \Pr\left[\mbox{\ensuremath{A_{mult}} wins}\right]} \\
& + \sum_{k=1}^{t-1} \overbrace{\sum_{d \in \{0,1\}} \Pr\left[A_{mult}\left(E_{pk}(m_0^1, \ldots, m_0^k, m_1^{k+1}, \ldots, m_1^t)\right)=d\right]}^{=1}
 \Bigg{)} \\
\mbox{(simplification)} = &\frac{1}{2t} \bigg{(} 2 \cdot \Pr\left[\mbox{\ensuremath{A_{mult}} wins}\right] + t-1 \bigg{)} \\
\mbox{(simplification)} = &\frac{1}{t} \Pr\left[\mbox{\ensuremath{A_{mult}} wins}\right] + \frac{1}{2} - \frac{1}{2t}
\end{align*}

Therefore:
\begin{align*}
\Pr\left[\mbox{\ensuremath{A_{mult}} wins}\right] 
\le t(\frac{1}{2} + \varepsilon - \frac{1}{2} + \frac{1}{2t})
= \frac{1}{2} + t \cdot \varepsilon
= \frac{1}{2} + \varepsilon_t
\ \ \ \ \ \square
\end{align*}

\section{} % 8

\subsection{} % 8.a
First, note that if $p,q$ are $n$ bit numbers, then $m=pq$ has at most $2n=O(n)$ bits.
Computing $a^{2^t}$ using iterated squaring involves $t$ steps of (modular) squaring a number in the range $[0,m-1]$: \[
a_0=a, a_1=a_0^2=a^2, a_2=a_1^2=a^{2^2}, a_3=a_2^2=a^{2^3}, \ldots, a_t=a_{t-1}^2=a^{2^t}
\]
Therefore the number of modular multiplications of $O(n)$ bit numbers is exactly $t$.

\subsection{} % 8.b
Knowing the factorization of $m$ allows us to compute $\phi(m)=(p-1)(q-1)$. Then, by Euler's theorem we know that $a^{2^t} \equiv a^{2^t \mod{\phi(m)}} \pmod{m}$. Therefore to compute $a^{2^t} \pmod{m}$ we need to calculate: \[
a_0=a, a_1=a_0^2=a^2, \ldots, a_k=a_{k-1}^2=a^{2^k}
\]
where $k$ is the number of bits of $2^t \mod \phi(m)$.
afterwards we multiply the elements according to the binary representation of $\phi(m)$.
$\phi(m)$ can have no more than $2n$ bits, therefore we need to perform at most $k+k = 2k \le 4n$ modular multiplications.
Note that if $2^t < \phi(m)$ then we resort to the first method and perform exactly $t$ multiplication. \\
So to summarize, we perform no more than $\min \{ t, 4n \}$ multiplications.

\end{document}